---
title: "Hong Kong Macroeconomic Data"
author: "Jason Herbaugh and Alexander Sepenu"
date: "11/29/2021"
output:
  pdf_document:
    toc: true

---



Import all libraries need for the Project.
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(nnfor)
library(forecast)
library(vars)
library(tswge)
library(naniar)
library(GGally)
library(RColorBrewer)

```


Data is available from: https://www.kaggle.com/stanley11291985/hk-macroeconomics-data


This data set is economic data for the Hong Kong private housing market collected between 2003 and 2019. 

The data contains variables connected to the following: 

* Hang Seng Index (total volume and close price)
* Index data for Consumer Price and Private Domestic Housing
* Unemployment Rate and Bank Interest Rate
* Inventory (built/sold/vacant)
* Sales Metrics (quantity/amount)



Read in the CSV file and perform summary statistics on the data.
There are no missing data or outliers in our data.
```{r Hong Kong Macroeconomic CSV Data}
hk_eco <- read.csv(file.choose(), header = TRUE)

head(hk_eco)

hk_eda <- hk_eco

str(hk_eda)

summary(hk_eda)


```


Produce a scatter plot of columns in our dataset. 
All Columns are continuous.
```{r GGPAirs, echo=FALSE}
ggpairs(hk_eda[2:14])
```


Univariate analysis on the HSI_Volume column. 
This is the transaction volume for the Hang Seng Index.
```{r Scale HSI_Volume, echo=FALSE}
#choosing hk_eda$HSI...volume to run Univarate Model
hk <- (hk_eco$HSI_volume)

#scale data by dividing by 1 million to normalize data
hk.scale <- hk_eco$HSI_volume/1000000

#plotting different time frames in data to game insight

plotts.sample.wge(hk.scale)

# True Acf is slowly dampening  with spectral density showing evidence of a wandering behavior at peak f=0 as seen in the realization 
# with a hint of cyclic behavior gives an indication of a dominant (1-B) present hence we proceed to difference the data


# Taking First difference to remove (1-B) from full  scaled data
hk.df1= artrans.wge(hk.scale,phi.tr = c(rep(0,364),1)) # differencing to remove seasonality to make the data more stationary

hk.df2 = artrans.wge(hk.df1,phi.tr = 1) #differencing the data to remove (1-b) factor and the sample auto-correlation appears not to look white noise  and but shows cyclic behavior.

```

Identification of the HSI_Volume for ARIMA/ARMA model identification.
```{r HSI_Volume Model ID, echo=FALSE}
# Model identification for the transformed or difference data using AIC and BIC approach
aic5.wge(hk.df1, p= 0:13, q= 0:5, type = "aic")

aic5.wge(hk.df1, p= 0:13, q= 0:5, type = "bic")

#BIC imposes a stronger penalty for increasing p and q and pick models with fewer parameters.
# To avoid overmodeeling, we use ARMA(2,2) from the BIC results

```

Estimation of the coefficients for the HSI_Volume for the ARIMA(2,1,2) model. 
```{r HSI_Volume Final Model, echo=FALSE}
ljung.wge(hk.df2)$pval #FTR Ho
ljung.wge(hk.df2, K = 48)$pval #FTR Ho

# Use estimate p & q to get estimates of phi and thetas
est.hk <- est.arma.wge(hk.df1,p=2, q=2)

est.hk$avar

mean(hk.scale) #1492.191

#Final Model is produced from above values:
# (1-B^12)(1 - 1.7383B + 0.7394B^2)(X_t + 1492.191) = (1 - 1.3420B + 0.3625B^2)a_t  $avar = 538864.1


```

Forecasts for the HSI_Volume ARMA(2,2) and ARMA(2,1,2) modelS ..
```{r HSI_Volume model forecast, echo=FALSE}
###### Short and Long term forecast

#ARMA(2,2)
ped.scale.sht1 = fore.arma.wge(hk.scale, phi = est.hk$phi,theta = est.hk$theta, n.ahead = 365, lastn = FALSE,limits = FALSE)
plot(ped.scale.sht1$f, type = "l")
plot(seq(1,4233,1), hk.scale, type = "l",xlim = c(0,4598), ylab = "HSI_volume", main = "HSI_volume 365 days Short Term Forecast Using ARMA(2,2)")
lines(seq(4234,4598,1), ped.scale.sht1$f, type = "l", col = "red") # stationary models have natural attraction towards the mean

#ARIMA(2,1,2)
ped.scale.sht2  = fore.aruma.wge(hk.scale, s=365,est.hk$phi,theta = est.hk$theta, n.ahead = 365, lastn = FALSE,limits = FALSE)
plot(ped.scale.sht2$f, type = "l")
plot(seq(1,4233,1), hk.scale, type = "l",xlim = c(0,4598), ylab = "HSI_volume", main = "HSI_volume 365 days Short Term Forecast Using ARIMA(2,1,2)")
lines(seq(4234,4598,1), ped.scale.sht2$f, type = "l", col = "red") 


#ARMA(2,2)
ped.scale.lng1 = fore.arma.wge(hk.scale, phi = est.hk$phi,theta = est.hk$theta, n.ahead = 1825, lastn = FALSE,limits = FALSE)
plot(ped.scale.lng1$f, type = "l")
plot(seq(1,4233,1), hk.scale, type = "l",xlim = c(0,6058), ylab = "HSI_volume", main = "HSI_volume 5 Years Long Term Forecast Using ARMA(2,2)")
lines(seq(4234,6058,1), ped.scale.lng1$f, type = "l", col = "red") # stationary models have natural attraction towards the mean

#ARIMA(2,1,2)
ped.scale.lng2 = fore.aruma.wge(hk.scale, s=365,est.hk$phi,theta = est.hk$theta, n.ahead = 1825, lastn = TRUE,limits = FALSE)
plot(ped.scale.lng2$f, type = "l")
plot(seq(1,4233,1), hk.scale, type = "l",xlim = c(0,6058), ylab = "HSI_volume", main = "HSI_volume 5 Years Long Term Forecast Using ARIMA(2,1,2)")
lines(seq(4234,6058,1), ped.scale.lng2$f, type = "l", col = "red")

```

Calculation of the ASE values for the HSI_Volume ARMA(2,2) and ARMA(2,1,2) modelS .
```{r HSI_Volume model ASE, echo=FALSE}
###### Calculating ASE for short and Long terms observations

#Calculating ASE for short term 365 days observations ARMA Model

n = 365
x = hk.scale
x.pred.scale1 = fore.arma.wge(hk.scale, phi = est.hk$phi,theta = est.hk$theta, n.ahead = 365, lastn = FALSE,limits = FALSE)
ASE.scale1 = mean((x[(length(x)-n+1):(length(x))]-x.pred.scale1$f)^2)
print(paste0('Short Term ARMA(2,2) ASE: ',round(ASE.scale1,2)))

# Short Term ARMA ASE: 271120.67

# Calculating ASE for short Terms 365 days observations of ARIMA model
n = 365
x = hk.scale
x.pred.scale2 = fore.aruma.wge(hk.scale,s=365,est.hk$phi,theta = est.hk$theta, n.ahead = 365, lastn = FALSE,limits = FALSE)
ASE.scale2 = mean((x[(length(x)-n+1):(length(x))]-x.pred.scale2$f)^2)
print(paste0('Short Term ARIMA(2,1,2) ASE: ',round(ASE.scale2,2)))

# Short Term ARIMA ASE Seasonal: 18729.93

# Calculating ASE for Long Term 1825 days (5 years) observations of ARMA model
n1 = 1825
x = hk.scale
x.pred.scale3 = fore.arma.wge(hk.scale, phi = est.hk$phi,theta = est.hk$theta, n.ahead = 1825, lastn = FALSE,limits = FALSE)
ASE.scale3 = mean((x[(length(x)-n1+1):(length(x))]-x.pred.scale3$f)^2)
print(paste0('Long Term ARMA(2,2) ASE: ',round(ASE.scale3,2)))

#Long Term ARMA ASE: 413770.67

# Calculating ASE for Long Term 1825 days (5 years) observations of ARIMA model
n1 = 1825
x = hk.scale
x.pred.scale4 = fore.aruma.wge(hk.scale,s=365,est.hk$phi,theta = est.hk$theta, n.ahead = 1825, lastn = FALSE,limits = FALSE)
ASE.scale4 = mean((x[(length(x)-n1+1):(length(x))]-x.pred.scale4$f)^2)
print(paste0('Long Term ARIMA(2,1,2) ASE: ',round(ASE.scale4,2)))



#Long Term ARIMA ASE: 538957.77
```

Calculation of the Rolling Window ASE for the HSI_Volume ARMA(2,2) and ARMA(2,1,2) modelS .
Please uncomment the Rolling_Window_ASE to run the Rolling Window ASE.
```{r HSI_Volume model Rolling Window ASE, include=FALSE}
#Rolling Window ASE

Rolling_Window_ASE = function(series, trainingSize, horizon = 1, s = 0, d = 0, phis = 0, thetas = 0)
{
  ASEHolder = numeric()
  
  for( i in 1:(length(series)-(trainingSize + horizon) + 1))
  {
    
    forecasts = fore.aruma.wge(series[i:(i+(trainingSize-1))],phi = phis, theta = thetas, s = s, d = d,n.ahead = horizon)
    
    ASE = mean((series[(trainingSize+i):(trainingSize+ i + (horizon) - 1)] - forecasts$f)^2)
    
    ASEHolder[i] = ASE
    
  }
  
  ASEHolder
  hist(ASEHolder)
  WindowedASE = mean(ASEHolder)
  
  print("The Summary Statistics for the Rolling Window ASE Are:")
  print(summary(ASEHolder))
  print(paste("The Rolling Window ASE is: ",WindowedASE))
  return(WindowedASE)
}

#ARMA Rolling ASE
#Rolling_Window_ASE(hk.scale, phis = est.hk$phi,thetas = est.hk$theta, horizon = 365, trainingSize = 500) 

#The Short Term Rolling Window ASE is: 645583.3


#ARIMA rOLLING ASE
#Rolling_Window_ASE(hk.scale,d=1, s = 365, phis = est.hk$phi,thetas = est.hk$theta, horizon = 1825, trainingSize = 1000) 

#The Short Term Rolling Window ASE is: 1558748


```


Comparison of the HSI_Volume ARMA(2,2) modeled against the generated realizations. 
```{r HSI_Volume Model Gen Realizations, echo=FALSE}
#Compare Generated Realizations 

hk.arma.gen = gen.arma.wge(1000,phi = est.hk$phi,theta = est.hk$theta, vara = est.hk$avar)

plotts.sample.wge(hk.arma.gen)


hk.arima.gen = gen.arima.wge(1000,d=1,s=365, phi = est.hk$phi,theta = est.hk$theta, vara = est.hk$avar)

plotts.sample.wge(hk.arima.gen)


### Testing parameterized model estimates 

#Comparing Spectral Densities using parameters from ARMA(2,2) model generated
sims = 2
SpecDen = parzen.wge(hk.scale, plot = "FALSE")
plot(SpecDen$freq,SpecDen$pzgram, type = "l", lwd = 2)

for( i in 1: sims)
{
  SpecDen2 = parzen.wge(gen.arma.wge(5000,phi = est.hk$phi,theta = est.hk$theta, vara = est.hk$avar, plot = "FALSE"), plot = "FALSE")
  lines(SpecDen2$freq,SpecDen2$pzgram, lwd = 2, col = "red")
} # Estimated parameters from generated model are pretty consistent with true parameters from the data

```



Univariate analysis on the HSI Private Domestic Price Index.
This is the Price Index of private housing in Hong Kong.
```{r Price_Index , echo=FALSE}
hk.ind <- hk_eda$Private_Domestic.Price_Index.


#plotting different time frames in data to game insight
plotts.sample.wge(hk.ind)# realization is shows wandering behavior with no sign of cyclic behavior
# it also has its True sample autocorrelation showing identical rho_k = 1
#spectral density shows a dominant (1-B) behavior at peak f=0 hence an indication for an ARIMA model we then proceed to take the first different 

# Taking First difference to remove (1-B^12) from full data
hk.ind.df1= artrans.wge(hk.ind,phi.tr = c(rep(0,364),1))# taking the 12th difference of the data (1-B^12) to stationarize the data but shows seasonality at lag 12 
#hence we remove the seasonality in the data with this differencing like in the airline model to make more stationary

acf(hk.ind.df1) # Acfs are slowing dumping with some dominant (1-B) Factor

hk.ind.df2= artrans.wge(hk.ind.df1,phi.tr = 1) #taking the second difference of the first difference to remove the (1-B) factor shows significance at lag 1 with hint of cyclic behavior

acf(hk.ind.df2)


plotts.sample.wge(hk.ind.df2) # sample Autocorrelations shows cyclic behavior at lag 1 and a slight sinusoidal behavior damping in the sample auto-correlation
#spectral density of the realization has a high peak at f=0 but has ripples between f=0 and f=0.5 worth noting

parzen.wge(hk.ind.df2) # wander with a strong indication of cyclic behavior
```

Identification of the Price Index for ARIMA/ARMA model identification.
```{r Price Index Model ID, echo=FALSE}
# Find a model for the transformed or difference data using AIC and BIC with the assumption data is stationary
aic5.wge(hk.ind.df2, p= 0:13, q= 0:5, type = "aic")

aic5.wge(hk.ind.df2, p= 0:13, q= 0:5, type = "bic")

```


Estimation of the coefficients for the Price Index for the ARIMA(11,2,4) model. 
```{r Price_Index Model, echo=FALSE}
# Use estimate p & q to get estimates of phi and thetas
est.hk.ind <- est.arma.wge(hk.ind.df2,p=11, q=4)

est.hk.ind$avar

mean(hk.ind)



#Final Model
# (1+1.1624B+0.9835B^2 (1 + 0.0322B - 0.3918B^2 - 1.1102B^3 + 0.0967B^4 + 0.0845B^5 + 0.0623B^6 + 0.0676B^7 + 0.0547B^8 + 0.0711B^9 + 0.0540B^10 + 0.0511B^11)(X_t + 197.065) = (1 - 0.7450B - 0.3282B^2 - 0.7976B^3 + 0.9230B^4)a_t  $avar = 0.1306278




```

Forecasts for the Price Index ARMA(11,4) AND ARIMA(11,2,4) models.
```{r Price Index model forecast, echo=FALSE}
###### Short and Long term forecast

#ARMA(11,4)
ped.ind.sht1 = fore.arma.wge(hk.ind, phi = est.hk.ind$phi,theta = est.hk.ind$theta, n.ahead = 365, lastn = FALSE,limits = FALSE)
plot(ped.ind.sht1$f, type = "l")
plot(seq(1,4233,1), hk.ind, type = "l",xlim = c(0,4598), ylab = "Private.Domestic.Price.Index", main = "Private.Domestic.Price.Index 365 days Short Term Forecast using ARMA(11,4)")
lines(seq(4234,4598,1), ped.ind.sht1$f, type = "l", col = "red")

#ARIMA(11,2,4)
ped.ind.sht2  = fore.aruma.wge(hk.ind,d=1,s=365,est.hk.ind$phi,theta = est.hk.ind$theta, n.ahead = 365, lastn = FALSE,limits = FALSE)
plot(ped.ind.sht2$f, type = "l")
plot(seq(1,4233,1), hk.ind, type = "l",xlim = c(0,4598), ylab = "Private.Domestic.Price.Index", main = "Private.Domestic.Price.Index 365 days Short Term Forecast using ARIMA(11,2,4)")
lines(seq(4234,4598,1), ped.ind.sht2$f, type = "l", col = "red")


#ARMA(11,4)
ped.ind.lng1 = fore.arma.wge(hk.ind, phi = est.hk.ind$phi,theta = est.hk.ind$theta, n.ahead = 1825, lastn = FALSE,limits = FALSE)
plot(ped.ind.lng1$f, type = "l")
plot(seq(1,4233,1), hk.ind, type = "l",xlim = c(0,6058), ylab = "Private.Domestic.Price.Index", main = "Private.Domestic.Price.Index 5 Years Long Term Forecast Using ARMA(11,4)")
lines(seq(4234,6058,1), ped.ind.lng1$f, type = "l", col = "red")

#ARIMA(11,2,4)
ped.ind.lng2 = fore.aruma.wge(hk.ind,d= 1, s=365,est.hk.ind$phi,theta = est.hk.ind$theta, n.ahead = 1825, lastn = FALSE,limits = FALSE)
plot(ped.ind.lng2$f, type = "l")
plot(seq(1,4233,1), hk.ind, type = "l",xlim = c(0,6058), ylab = "Private.Domestic.Price.Index", main = "Private.Domestic.Price.Index 5 Years Long Term Forecast Using ARIMA(11,2,4)")
lines(seq(4234,6058,1), ped.ind.lng2$f, type = "l", col = "red")

```


Calculation of the ASE values for the Price_Index ARMA(11,4) AND ARIMA(11,2,4) models.
```{r Price_Volume model ASE, echo=FALSE}
##### Calculating ASE for short and Long terms observations

#Calculating ASE for short term 365 days observations

# Calculating ASE for Short Term 365 days observations of ARMA model
n = 365
x = hk.ind
x.pred.ind1 = fore.arma.wge(hk.ind, phi = est.hk.ind$phi,theta = est.hk.ind$theta, n.ahead = 365, lastn = FALSE,limits = FALSE)
ASE.ind1 = mean((x[(length(x)-n+1):(length(x))]-x.pred.ind1$f)^2)
print(paste0('Short Term ARMA(11,4) ASE: ',round(ASE.ind1,2)))

# Short Term ARMA(11,4) ASE: 29985.79

# Calculating ASE for Short Term 365 days observations of ARIMA model
n = 365
x = hk.ind
x.pred.ind2 = fore.aruma.wge(hk.ind,s=365,est.hk.ind$phi,theta = est.hk.ind$theta, n.ahead = 365, lastn = FALSE,limits = FALSE)
ASE.ind2 = mean((x[(length(x)-n+1):(length(x))]-x.pred.ind2$f)^2)
print(paste0('Short Term ARIMA(11,2,4) ASE: ',round(ASE.ind2,2)))

# Short Term ARIMA(11,2,4) ASE: 104.97


# Calculating ASE for Long Term 1825 days observations of ARMA model
n1 = 1825
x = hk.ind
x.pred.ind3 = fore.arma.wge(hk.ind, phi = est.hk.ind$phi,theta = est.hk.ind$theta, n.ahead = 1825, lastn = FALSE,limits = FALSE)
ASE.ind3 = mean((x[(length(x)-n1+1):(length(x))]-x.pred.ind3$f)^2)
print(paste0('Long Term ARMA(11,4) ASE: ',round(ASE.ind3,2)))

#Long Term ARMA(11,4) ASE: 14794.49


# Calculating ASE for Long Term 1825 days observations of ARIMA model
n1 = 1825
x = hk.ind
x.pred.ind4 = fore.aruma.wge(hk.ind,s=365,est.hk.ind$phi,theta = est.hk.ind$theta, n.ahead = 1825, lastn = FALSE,limits = FALSE)
ASE.ind4 = mean((x[(length(x)-n1+1):(length(x))]-x.pred.ind4$f)^2)
print(paste0('Long Term ARIMA(11,2,4) ASE: ',round(ASE.ind4,2)))
#Long Term ARIMA(11,2,4) ASE: 8384.81

```




Calculation of the Rolling Window ASE for the Price_Index ARIMA(11,2,4) model .
Please uncomment the Rolling_Window_ASE to run the Rolling Window ASE.
```{r Price_Volume model Rolling Windos ASE, include=FALSE}
#Rolling Window ASE

Rolling_Window_ASE = function(series, trainingSize, horizon = 1, s = 0, d = 0, phis = 0, thetas = 0)
{
  ASEHolder = numeric()
  
  for( i in 1:(length(series)-(trainingSize + horizon) + 1))
  {
    
    forecasts = fore.aruma.wge(series[i:(i+(trainingSize-1))],phi = phis, theta = thetas, s = s, d = d,n.ahead = horizon)
    
    ASE = mean((series[(trainingSize+i):(trainingSize+ i + (horizon) - 1)] - forecasts$f)^2)
    
    ASEHolder[i] = ASE
    
  }
  
  ASEHolder
  hist(ASEHolder)
  WindowedASE = mean(ASEHolder)
  
  print("The Summary Statistics for the Rolling Window ASE Are:")
  print(summary(ASEHolder))
  print(paste("The Rolling Window ASE is: ",WindowedASE))
  return(WindowedASE)
}

#ARMA Rolling ASE
#Rolling_Window_ASE(hk.ind, phis = est.hk.ind$phi,thetas = est.hk.ind$theta, horizon = 365, trainingSize = 500) 

#The Short Term Rolling Window ASE is: 1677.426


#ARIMA rOLLING ASE
#Rolling_Window_ASE(hk.ind, d=2, s = 365, phis = est.hk.ind$phi,thetas = est.hk.ind$theta, horizon = 1825, trainingSize = 1000) 

#The Short Term Rolling Window ASE is: 38524175


```


Comparison of the Price_Index ARIMA(11,2,4) modeled against the generated realizations. 
```{r Price Index Final Model, echo=FALSE}
### Testing parameterized model estimates

#Compare Generated Realizations and Spectral Densities 

hk.ind.arma.gen = gen.arma.wge(5000,phi = est.hk.ind$phi,theta = est.hk.ind$theta, vara = est.hk.ind$avar)

plotts.sample.wge(hk.ind.arma.gen)


hk.ind.arima.gen = gen.arima.wge(5000,d=2, s=365, phi = est.hk.ind$phi,theta = est.hk.ind$theta, vara = est.hk.ind$avar)

plotts.sample.wge(hk.ind.arima.gen)



#Compare Spectral Densities using parameters from ARIMA(11,2,4) model generated
sims = 2
SpecDen = parzen.wge(hk.ind, plot = "FALSE")
plot(SpecDen$freq,SpecDen$pzgram, type = "l", lwd = 2)

for( i in 1: sims)
{
  SpecDen2 = parzen.wge(gen.arima.wge(10000,d=2, s=365, phi = est.hk.ind$phi,theta = est.hk.ind$theta, vara = est.hk.ind$avar, plot = "FALSE"), plot = "FALSE")
  lines(SpecDen2$freq,SpecDen2$pzgram, lwd = 2, col = "red")
} 

## Estimated parameters from generated model are pretty consistent with with the actual parameters from the data 
```

Vector Autoregressive (VAR) models to allow for Multivariate models. 
Explanatory variables are Price_Index , First_Hand_Sales_Amount, and HSI_Volume.
Verify how these variables affect each other in a short term and long term model.
```{r Var Model Differencing, echo=FALSE}

#Read in our variables for the VAR Model
hk_vol <- hk_eco$HSI_volume
hk_ind <- hk_eco$Private_Domestic.Price_Index.
hk_sal_amt <- hk_eco$First_hand_sales_amount



##### Taking First Difference of data variables
hk_vol_df1 <- artrans.wge(hk_vol,phi.tr = c(rep(0,364),1))
hk_ind_df1 <- artrans.wge(hk_ind,phi.tr = c(rep(0,364),1))
hk_sal_amt_df1 <- artrans.wge(hk_sal_amt,phi.tr = c(rep(0,364),1))


######## Taking Second difference of data Variables
hk_vol_df2 <- artrans.wge(hk_vol_df1,phi.tr = 1)
hk_ind_df2 <- artrans.wge(hk_ind_df1,phi.tr = 1)
hk_sal_amt_df2 <- artrans.wge(hk_sal_amt_df1,phi.tr = 1)
```

Modeling a VAR Model for a Short Term Forecast (1 year).
```{r VAR Short Term model, echo=FALSE}
################################## VAR Model for Short Term

#VARSelect on Differenced Data chooses BIC = 12
VARselect(cbind(hk_vol_df2, hk_ind_df2, hk_sal_amt_df2),lag.max = 20, type = "both")

###BIC= (SC(n)) = 7.205915e+01 for p = 11

#VAR with p = 11
hk.VAR.st = VAR(cbind(hk_vol_df2, hk_ind_df2, hk_sal_amt_df2),type = "both",p = 11)


hk.pred.st = predict(hk.VAR.st,n.ahead=365,lastn= TRUE, ci = 0.95)


#We have predicted differences .... calculate actual Hong Kong HSI Volune
startingpoint.st = hk_vol[3869:4233]
hk.vol.fore.st = hk.pred.st$fcst$hk_vol[,1:3] + startingpoint.st

length(hk.vol.fore.st)

#Plot

plot(seq(1,4233,1), hk_vol, type = "l",xlim = c(0,4233), ylab = "Hong Kong HSI Vol", main = "VAR Model Short Term Forecast for Hong Kong Housing Index Volume")
lines(seq(3869,4233,1), hk.vol.fore.st[,1], type = "l", col = "red")

#Forecast each of the variables contained in the VAR model
fanchart(hk.pred.st, colors = brewer.pal(n = 8, name = "Blues"))


#Find Short Term VAR ASE
VAR.ASE.st = mean((hk_vol[3869:4233] - hk.vol.fore.st[,1])^2)

VAR.ASE.st
```

Modeling a VAR Model for a Long Term Forecast (5 years).
```{r VAR Long Term Model, echo=FALSE}

#VARSelect on Differenced Data chooses BIC = 12
VARselect(cbind(hk_vol_df2, hk_ind_df2, hk_sal_amt_df2),lag.max = 15, type = "both")

#AIC= 7.213653e+01 for p = 15

#VAR with p = 15
hk.VAR.lg = VAR(cbind(hk_vol_df2, hk_ind_df2, hk_sal_amt_df2),type = "both",p = 15)

hk.pred.lg = predict(hk.VAR.lg,n.ahead=1825,lastn= TRUE, ci = 0.95)


#We have predicted differences .... calculate actual Hong Kong HSI Volune
startingpoint.lg = hk_vol[2409:4233]
hk_hsi_for.lg = hk.pred.lg$fcst$hk_vol[,1:3] + startingpoint.lg


#Plot
plot(seq(1,4233,1), hk_vol, type = "l",xlim = c(0,4233), ylab = "Hong Kong HSI Volume", main = "Hong Kong Housing Index Volume Long Term Forecast")
lines(seq(2409,4233,1), hk_hsi_for.lg[,1], type = "l", col = "red")

#Forecast each of the variables contained in the VAR model
fanchart(hk.pred.lg, colors = brewer.pal(n = 8, name = "Blues")) # Change color pallet to make distinguishable.



#Find Long Term VAR ASE
VAR.ASE.lg = mean((hk_vol[2409:4233] - hk_hsi_for.lg[,1])^2)

VAR.ASE.lg


```


Multi-Layer Perceptron (MLP) using neural networks to model the data.
```{r MLP Data Prep, echo=FALSE}
#Prepare data by reading in data frame for short and long term MLP
hk_eco1 <- hk_eco[2:14]

hk.st <- hk_eco1[1:3867,]

hk.lg <- hk_eco1[1:2408,]

#Read all data into data frame for Regressors
hk.all <- hk_eco1[1:4233,]

#Read in Price_Index and First_Hand_Sales_amount as regressors for MLP
#Creates Data Frame of TS objects
hk.all.df <- data.frame(hk.ind=ts(hk.all$Private_Domestic.Price_Index.), hk.sale.amt=ts(hk.all$First_hand_sales_amount))

hk.mlp.df.st <- data.frame(hk.ind=ts(hk.st$Private_Domestic.Price_Index.), hk.sale.amt=ts(hk.st$First_hand_sales_amount))

hk.mlp.df.lg <- data.frame(hk.ind=ts(hk.lg$Private_Domestic.Price_Index.), hk.sale.amt=ts(hk.lg$First_hand_sales_amount))


```

Model Fitting for the Short Term (1 year) MLP Model.
```{r MLP Model Fit Short, echo=FALSE}


###### Fitting the MLP Model on Hong Kong Housing Index Volume for Short Term
#Optimal value for Repetitions is 7. Other values produce empty matrix.
fit.hk.mlp.st <- mlp(ts(hk.st$HSI_volume),reps=2, difforder= c(1,365),comb = "median", xreg = hk.mlp.df.st, det.type = "auto", sel.lag = TRUE )


fit.hk.mlp.st 

#### Plot the fitted model on Hong Kong Housing Index Volume using MLP Approach Short Term
plot(fit.hk.mlp.st)
```


Model Fitting for the Long Term (5 years) MLP Model.
```{r MLP Model Fit Long, echo=FALSE}


###### Fitting the MLP Model on Hong Kong Housing Index Volume for Long Term 
fit.hk.mlp.lg <- mlp(ts(hk.lg$HSI_volume), reps = 20, difforder= c(1,1825), comb = "median", xreg = hk.mlp.df.lg, det.type = "auto", sel.lag = TRUE  )

fit.hk.mlp.lg



####### Plot the fitted model on Hong Kong Housing Index Volume using MLP Approach Long Term
plot(fit.hk.mlp.lg)


```


Model Forecasting for the Short Term (1 year) MLP Model.
This shows every forecast with the MLP algorithm.
```{r MLP Model Forecast Short, echo=FALSE}


######## Short Term Forecast using MLP Approach
hk.fore.st = forecast(fit.hk.mlp.st, h = 365,xreg = hk.all.df)
plot(hk.fore.st)
```


MLP Model Forecasting for the Long Term (5 years) MLP Model.
This shows every forecast with the MLP algorithm.
```{r MLP Model Forecast Long, echo=FALSE}


### Long Term Forecast using MLP Approach
hk.fore.lg = forecast(fit.hk.mlp.lg, h = 1825, xreg = hk.all.df)

plot(hk.fore.lg)



```


ASE Model calculation for the Short Term (1 year) MLP Model.
```{r MLP Model ASE Short, echo=FALSE}


########### Calculating short term ASE for Hong Kong House Index Volume
ASE.mlp.st = mean((hk_eco$HSI_volume[3869:4233] - hk.fore.st$mean)^2)

ASE.mlp.st


```

ASE Model calculation for the Long Term (5 years) MLP Model.
```{r MLP Model ASE Long, echo=FALSE}

##### Calculating long term ASE for Hong Kong House Index Volume
ASE.mlp.lg = mean((hk_eco$HSI_volume[2409:4233] - hk.fore.lg$mean)^2)

ASE.mlp.lg

```

Model forecast for the short term (1 year) MLP Model.
```{r MLP Model forecast short, echo=FALSE}
#### Plot for short term forecast
plot(seq(1,4233,1), hk_eco$HSI_volume, type = "l",xlim = c(0,4233), ylab = "Hong Kong HSI Volume", main = "Short Term Forecast for Hong Kong Housing Index Volume ")
lines(seq(3869,4233,1), hk.fore.st$mean, type = "l", col = "red")
```

Model forecast for the long term (5 years) MLP Model.
```{r MLP Model forecast Long, echo=FALSE}
#### Plot for long term forecast
plot(seq(1,4233,1), hk_eco$HSI_volume, type = "l",xlim = c(0,4233),  ylim = c(-14000000000,10000000000),ylab = "Hong Kong HSI Volume", main = "Long Term Forecast for Hong Kong Housing Index Volume")
lines(seq(2409,4233,1), hk.fore.lg$mean, type = "l", col = "red")


```


Ensemble models combining the MLP and VAR models to produce a new model.
Short Term Ensemble model.
```{r Ensemble Short term , echo=FALSE}
ensemble.st  = (hk.vol.fore.st[,1] + hk.fore.st$mean)/2


##### Short Ensemble ASE
ASE.ens.st = mean((hk_eco$HSI_volume[3869:4233] - ensemble.st)^2)

ASE.ens.st

############## Plot Short Term Ensemble
plot(hk_eco$HSI_volume, type = "l")
lines(seq(3869,4233,1),ensemble.st,col = "green")


##############################Plot for Short Term Ensemble Forecast
plot(seq(1,4233,1), hk_eco$HSI_volume, type = "l",xlim = c(0,4233), ylab = "Hong Kong HSI Volume", main = "Short Term Ensemble Forecast")
lines(seq(3869,4233,1), ensemble.st, type = "l", col = "red")



```




Ensemble models combining the MLP and VAR models to produce a new model.
Long Term Ensemble model.
```{r Ensemble Long term , echo=FALSE}
ensemble.lg  = (hk_hsi_for.lg[,1] + hk.fore.lg$mean)/2


######### Long Ensemble ASE
ASE.ens.lg = mean((hk_eco$HSI_volume[3869:4233] - ensemble.lg)^2)

ASE.ens.lg

#### Plot Short Term Ensemble
plot(hk_eco$HSI_volume, type = "l")
lines(seq(2409,4233,1),ensemble.lg,col = "green")


########### Plot for Short Term Ensemble Forecast
plot(seq(1,4233,1), hk_eco$HSI_volume, type = "l",xlim = c(0,4233), ylab = "Hong Kong HSI Volume", main = "Long Term Ensemble Forecast")
lines(seq(2409,4233,1), ensemble.lg, type = "l", col = "purple")

```
