---
title: "Hong Kong Macroeconomic Data"
author: "Jason Herbaugh and Alexander Sepenu"
date: "11/13/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(nnfor)
library(forecast)
library(vars)
library(tswge)
library(naniar)
library(DataExplorer)
library(GGally)
```

Data is available from: https://www.kaggle.com/stanley11291985/hk-macroeconomics-data

This data set is economic data for the Hong Kong private housing market collected between 2003 and 2019. The data contains variables connected to the following: 

* Hang Seng Index (total volume and close price)
* Index data for Consumer Price and Private Domestic Housing
* Unemployment Rate and Bank Interest Rate
* Inventory (built/sold/vacant)
* Sales Metrics (quantity/amount)


```{r Hong Kong Macroeconomic CSV Data}
hk_eco <- read.csv(file.choose(), header = TRUE)

head(hk_eco)

hk_eda <- hk_eco

str(hk_eda)

summary(hk_eda)


```


Scatter Plot of columns. All Columns are continous.
```{r GGPAirs, echo=FALSE}
ggpairs(hk_eda[2:14])
```


Univariate analysis on the HSI_Volume column. This is the transaction volume for the Hang Seng Index.
```{r Scale HSI_Volume, echo=FALSE}
#choosing hk_eda$HSI...volume to run Univarate Model
hk <- (hk_eco$HSI_volume)

#scale data by dividing by 1 million to normalize data
hk.scale <- hk_eco$HSI_volume/1000000

#plotting different timeframes in data to game insight
plotts.sample.wge(hk.scale)# True Acf is slowly dumping  with spectral density showing evidence of a wandering behavior at peak f=0 as seen in the realization 
# with a hint of cyclic behavior gives an indication of a dominant (1-B) present hence we proceed to difference the data


# Taking First difference to remove (1-B) from full  scaled data
hk.df1= artrans.wge(hk.scale,phi.tr = c(rep(0,364),1)) # differencing to remove seasonality to make the data more stationary

hk.df2 = artrans.wge(hk.df1,phi.tr = 1)#differencing the data to remove (1-b) factor and the sample auto-correlation appears not to look white noise  and but shows cyclic behavior.

# we will proceed to model the data
```

HSI_Volume model identification
```{r HSI_Volume Model ID, echo=FALSE}
# Model identification for the transformed or difference data using AIC and BIC approach
aic5.wge(hk.df1, p= 0:13, q= 0:5, type = "aic")

aic5.wge(hk.df1, p= 0:13, q= 0:5, type = "bic")

# Since AIC value is lower compared to that of BIC, we use ARMA(3,4) from the AIC results

```

HSI_Volume estimate coefficients for model. 
```{r HSI_Volume Final Model, echo=FALSE}
#ljung.wge(hk.df2)$pval #FTR Ho
#ljung.wge(hk.df2, K = 48)$pval #FTR Ho

# Use estimate p & q to get estimates of phi and thetas
est.hk <- est.arma.wge(hk.df1,p=2, q=2)

est.hk$avar

mean(hk.scale) #1492.191

#Final Model
# (1-B^12)(1 - 1.7383B + 0.7394B^2)(X_t + 1492.191) = (1 - 1.3420B + 0.3625B^2)a_t  $avar = 538864.1


```

HSI_Volume model forecasts
```{r HSI_Volume model forecast, echo=FALSE}
###### Short and Long term forecast

#ARMA(2,2)
ped.scale.sht1 = fore.arma.wge(hk.scale, phi = est.hk$phi,theta = est.hk$theta, n.ahead = 365, lastn = FALSE,limits = FALSE)
plot(ped.scale.sht1$f, type = "l")
plot(seq(1,4233,1), hk.scale, type = "l",xlim = c(0,4598), ylab = "HSI_volume", main = "HSI_volume 365 days Short Term Forecast Using ARMA(2,2)")
lines(seq(4234,4598,1), ped.scale.sht1$f, type = "l", col = "red") # stationary models have natural attraction towards the mean

#ARIMA(2,1,2)
ped.scale.sht2  = fore.aruma.wge(hk.scale, s=365,est.hk$phi,theta = est.hk$theta, n.ahead = 365, lastn = FALSE,limits = FALSE)
plot(ped.scale.sht2$f, type = "l")
plot(seq(1,4233,1), hk.scale, type = "l",xlim = c(0,4598), ylab = "HSI_volume", main = "HSI_volume 365 days Short Term Forecast Using ARIMA(2,1,2)")
lines(seq(4234,4598,1), ped.scale.sht2$f, type = "l", col = "red") 


#ARMA(2,2)
ped.scale.lng1 = fore.arma.wge(hk.scale, phi = est.hk$phi,theta = est.hk$theta, n.ahead = 1825, lastn = FALSE,limits = FALSE)
plot(ped.scale.lng1$f, type = "l")
plot(seq(1,4233,1), hk.scale, type = "l",xlim = c(0,6058), ylab = "HSI_volume", main = "HSI_volume 5 Years Long Term Forecast Using ARMA(2,2)")
lines(seq(4234,6058,1), ped.scale.lng1$f, type = "l", col = "red") # stationary models have natural attraction towards the mean

#ARIMA(2,1,2)
ped.scale.lng2 = fore.aruma.wge(hk.scale, s=365,est.hk$phi,theta = est.hk$theta, n.ahead = 1825, lastn = TRUE,limits = FALSE)
plot(ped.scale.lng2$f, type = "l")
plot(seq(1,4233,1), hk.scale, type = "l",xlim = c(0,6058), ylab = "HSI_volume", main = "HSI_volume 5 Years Long Term Forecast Using ARIMA(2,1,2)")
lines(seq(4234,6058,1), ped.scale.lng2$f, type = "l", col = "red")

```

HSI_Volume model ASE
```{r HSI_Volume model ASE, echo=FALSE}
###### Calculating ASE for short and Long terms observations

#Calculating ASE for short term 365 days observations ARMA Model

n = 365
x = hk.scale
x.pred.scale1 = fore.arma.wge(hk.scale, phi = est.hk$phi,theta = est.hk$theta, n.ahead = 365, lastn = FALSE,limits = FALSE)
ASE.scale1 = mean((x[(length(x)-n+1):(length(x))]-x.pred.scale1$f)^2)
print(paste0('Short Term ARMA(2,2) ASE: ',round(ASE.scale1,2)))

# Short Term ARMA ASE: 271120.67

# Calculating ASE for short Terms 365 days observations of ARIMA model
n = 365
x = hk.scale
x.pred.scale2 = fore.aruma.wge(hk.scale,s=365,est.hk$phi,theta = est.hk$theta, n.ahead = 365, lastn = FALSE,limits = FALSE)
ASE.scale2 = mean((x[(length(x)-n+1):(length(x))]-x.pred.scale2$f)^2)
print(paste0('Short Term ARIMA(2,1,2) ASE: ',round(ASE.scale2,2)))

# Short Term ARIMA ASE Seasonal: 18729.93

# Calculating ASE for Long Term 1825 days (5 years) observations of ARMA model
n1 = 1825
x = hk.scale
x.pred.scale3 = fore.arma.wge(hk.scale, phi = est.hk$phi,theta = est.hk$theta, n.ahead = 1825, lastn = FALSE,limits = FALSE)
ASE.scale3 = mean((x[(length(x)-n1+1):(length(x))]-x.pred.scale3$f)^2)
print(paste0('Long Term ARMA(2,2) ASE: ',round(ASE.scale3,2)))

#Long Term ARMA ASE: 2413770.67

# Calculating ASE for Long Term 1825 days (5 years) observations of ARIMA model
n1 = 1825
x = hk.scale
x.pred.scale4 = fore.aruma.wge(hk.scale,s=365,est.hk$phi,theta = est.hk$theta, n.ahead = 1825, lastn = FALSE,limits = FALSE)
ASE.scale4 = mean((x[(length(x)-n1+1):(length(x))]-x.pred.scale4$f)^2)
print(paste0('Long Term ARIMA(2,1,2) ASE: ',round(ASE.scale4,2)))



#Long Term ARIMA ASE: 538957.77
```

HSI_Volume model Rolling Window ASE
```{r Price_Volume model ASE, include=FALSE}
#Rolling Window ASE

Rolling_Window_ASE = function(series, trainingSize, horizon = 1, s = 0, d = 0, phis = 0, thetas = 0)
{
  ASEHolder = numeric()
  
  for( i in 1:(length(series)-(trainingSize + horizon) + 1))
  {
    
    forecasts = fore.aruma.wge(series[i:(i+(trainingSize-1))],phi = phis, theta = thetas, s = s, d = d,n.ahead = horizon)
    
    ASE = mean((series[(trainingSize+i):(trainingSize+ i + (horizon) - 1)] - forecasts$f)^2)
    
    ASEHolder[i] = ASE
    
  }
  
  ASEHolder
  hist(ASEHolder)
  WindowedASE = mean(ASEHolder)
  
  print("The Summary Statistics for the Rolling Window ASE Are:")
  print(summary(ASEHolder))
  print(paste("The Rolling Window ASE is: ",WindowedASE))
  return(WindowedASE)
}

#ARMA Rolling ASE
Rolling_Window_ASE(hk.scale, phis = est.hk$phi,thetas = est.hk$theta, horizon = 365, trainingSize = 500) 

#The Short Term Rolling Window ASE is: 645583.3


#ARIMA rOLLING ASE
Rolling_Window_ASE(hk.scale,d=1, s = 365, phis = est.hk$phi,thetas = est.hk$theta, horizon = 1825, trainingSize = 1000) 

#The Short Term Rolling Window ASE is: 1558748


```


HSI_Volume compare generated realizations. 
```{r HSI_Volume Final Model, echo=FALSE}
#Compare Generated Realizations 

hk.arma.gen = gen.arma.wge(1000,phi = est.hk$phi,theta = est.hk$theta, vara = est.hk$avar)

plotts.sample.wge(hk.arma.gen)


hk.arima.gen = gen.arima.wge(1000,d=1,s=365, phi = est.hk$phi,theta = est.hk$theta, vara = est.hk$avar)

plotts.sample.wge(hk.arima.gen)


### Testing parameterized model estimates 

#Comparing Spectral Densities using parameters from ARMA(2,2) model generated
sims = 2
SpecDen = parzen.wge(hk.scale, plot = "FALSE")
plot(SpecDen$freq,SpecDen$pzgram, type = "l", lwd = 2)

for( i in 1: sims)
{
  SpecDen2 = parzen.wge(gen.arma.wge(5000,phi = est.hk$phi,theta = est.hk$theta, vara = est.hk$avar, plot = "FALSE"), plot = "FALSE")
  lines(SpecDen2$freq,SpecDen2$pzgram, lwd = 2, col = "red")
} # Estimated parameters from generated model are pretty consistent with true parameters from the data

```





Univariate analysis on the HSI Private Domestic Price Index This is the Price Index of private housing in Hong Kong.
```{r Price_Index , echo=FALSE}
hk.ind <- hk_eda$Private_Domestic.Price_Index.


#plotting different time frames in data to game insight
plotts.sample.wge(hk.ind)# realization is shows wandering behavior with no sign of cyclic behavior
# it also has its True sample autocorrelation showing identical rho_k = 1
#spectral density shows a dominant (1-B) behavior at peak f=0 hence an indication for an ARIMA model we then proceed to take the first different 

# Taking First difference to remove (1-B^12) from full data
hk.ind.df1= artrans.wge(hk.ind,phi.tr = c(rep(0,364),1))# taking the 12th difference of the data (1-B^12) to stationarize the data but shows seasonality at lag 12 
#hence we remove the seasonality in the data with this differencing like in the airline model to make more stationary

acf(hk.ind.df1) # Acfs are slowing dumping with some dominant (1-B) Factor

hk.ind.df2= artrans.wge(hk.ind.df1,phi.tr = 1) #taking the second difference of the first difference to remove the (1-B) factor shows significance at lag 1 with hint of cyclic behavior

acf(hk.ind.df2)


plotts.sample.wge(hk.ind.df2) # sample Autocorrelations shows cyclic behavior at lag 1 and a slight sinusoidal behavior damping in the sample auto-correlation
#spectral density of the realization has a high peak at f=0 but has ripples between f=0 and f=0.5 worth noting

parzen.wge(hk.ind.df2) # wander with a strong indication of cyclic behavior
```


Price Index model identification
```{r Price Index Model ID, echo=FALSE}
# Find a model for the transformed or difference data using AIC and BIC with the assumption data is stationary
aic5.wge(hk.ind.df2, p= 0:13, q= 0:5, type = "aic")

aic5.wge(hk.ind.df2, p= 0:13, q= 0:5, type = "bic")

```


Price Index estimate coefficients for model. 
```{r Price_Index Model, echo=FALSE}
# Use estimate p & q to get estimates of phi and thetas
est.hk.ind <- est.arma.wge(hk.ind.df2,p=11, q=4)

est.hk.ind$avar

mean(hk.ind)



#Final Model
# (1+1.1624B+0.9835B^2 (1 + 0.0322B - 0.3918B^2 - 1.1102B^3 + 0.0967B^4 + 0.0845B^5 + 0.0623B^6 + 0.0676B^7 + 0.0547B^8 + 0.0711B^9 + 0.0540B^10 + 0.0511B^11)(X_t + 197.065) = (1 - 0.7450B - 0.3282B^2 - 0.7976B^3 + 0.9230B^4)a_t  $avar = 0.1306278




```


Price Index model forecasts
```{r Price Index model forecast, echo=FALSE}
###### Short and Long term forecast

#ARMA(11,4)
ped.ind.sht1 = fore.arma.wge(hk.ind, phi = est.hk.ind$phi,theta = est.hk.ind$theta, n.ahead = 365, lastn = FALSE,limits = FALSE)
plot(ped.ind.sht1$f, type = "l")
plot(seq(1,4233,1), hk.ind, type = "l",xlim = c(0,4598), ylab = "Private.Domestic.Price.Index", main = "Private.Domestic.Price.Index 365 days Short Term Forecast using ARMA(11,4)")
lines(seq(4234,4598,1), ped.ind.sht1$f, type = "l", col = "red")

#ARIMA(11,2,4)
ped.ind.sht2  = fore.aruma.wge(hk.ind,d=1,s=365,est.hk.ind$phi,theta = est.hk.ind$theta, n.ahead = 365, lastn = FALSE,limits = FALSE)
plot(ped.ind.sht2$f, type = "l")
plot(seq(1,4233,1), hk.ind, type = "l",xlim = c(0,4598), ylab = "Private.Domestic.Price.Index", main = "Private.Domestic.Price.Index 365 days Short Term Forecast using ARIMA(11,2,4)")
lines(seq(4234,4598,1), ped.ind.sht2$f, type = "l", col = "red")


#ARMA(11,4)
ped.ind.lng1 = fore.arma.wge(hk.ind, phi = est.hk.ind$phi,theta = est.hk.ind$theta, n.ahead = 1825, lastn = FALSE,limits = FALSE)
plot(ped.ind.lng1$f, type = "l")
plot(seq(1,4233,1), hk.ind, type = "l",xlim = c(0,6058), ylab = "Private.Domestic.Price.Index", main = "Private.Domestic.Price.Index 5 Years Long Term Forecast Using ARMA(11,4)")
lines(seq(4234,6058,1), ped.ind.lng1$f, type = "l", col = "red")

#ARIMA(11,2,4)
ped.ind.lng2 = fore.aruma.wge(hk.ind,d= 1, s=365,est.hk.ind$phi,theta = est.hk.ind$theta, n.ahead = 1825, lastn = FALSE,limits = FALSE)
plot(ped.ind.lng2$f, type = "l")
plot(seq(1,4233,1), hk.ind, type = "l",xlim = c(0,6058), ylab = "Private.Domestic.Price.Index", main = "Private.Domestic.Price.Index 5 Years Long Term Forecast Using ARIMA(11,2,4)")
lines(seq(4234,6058,1), ped.ind.lng2$f, type = "l", col = "red")

```


Price_Volume model ASE
```{r Price_Volume model ASE, echo=FALSE}
##### Calculating ASE for short and Long terms observations

#Calculating ASE for short term 365 days observations

# Calculating ASE for Short Term 365 days observations of ARMA model
n = 365
x = hk.ind
x.pred.ind1 = fore.arma.wge(hk.ind, phi = est.hk.ind$phi,theta = est.hk.ind$theta, n.ahead = 365, lastn = FALSE,limits = FALSE)
ASE.ind1 = mean((x[(length(x)-n+1):(length(x))]-x.pred.ind1$f)^2)
print(paste0('Short Term ARMA(11,4) ASE: ',round(ASE.ind1,2)))

# Short Term ARMA(11,4) ASE: 29985.79

# Calculating ASE for Short Term 365 days observations of ARIMA model
n = 365
x = hk.ind
x.pred.ind2 = fore.aruma.wge(hk.ind,s=365,est.hk.ind$phi,theta = est.hk.ind$theta, n.ahead = 365, lastn = FALSE,limits = FALSE)
ASE.ind2 = mean((x[(length(x)-n+1):(length(x))]-x.pred.ind2$f)^2)
print(paste0('Short Term ARIMA(11,2,4) ASE: ',round(ASE.ind2,2)))

# Short Term ARIMA(11,2,4) ASE: 104.97


# Calculating ASE for Long Term 1825 days observations of ARMA model
n1 = 1825
x = hk.ind
x.pred.ind3 = fore.arma.wge(hk.ind, phi = est.hk.ind$phi,theta = est.hk.ind$theta, n.ahead = 1825, lastn = FALSE,limits = FALSE)
ASE.ind3 = mean((x[(length(x)-n1+1):(length(x))]-x.pred.ind3$f)^2)
print(paste0('Long Term ARMA(11,4) ASE: ',round(ASE.ind3,2)))

#Long Term ARMA(11,4) ASE: 14794.49


# Calculating ASE for Long Term 1825 days observations of ARIMA model
n1 = 1825
x = hk.ind
x.pred.ind4 = fore.aruma.wge(hk.ind,s=365,est.hk.ind$phi,theta = est.hk.ind$theta, n.ahead = 1825, lastn = FALSE,limits = FALSE)
ASE.ind4 = mean((x[(length(x)-n1+1):(length(x))]-x.pred.ind4$f)^2)
print(paste0('Long Term ARIMA(11,2,4) ASE: ',round(ASE.ind4,2)))
#Long Term ARIMA(11,2,4) ASE: 8384.81

```





Price_Volume model Rolling Window ASE
```{r Price_Volume model ASE, include=FALSE}
#Rolling Window ASE

Rolling_Window_ASE = function(series, trainingSize, horizon = 1, s = 0, d = 0, phis = 0, thetas = 0)
{
  ASEHolder = numeric()
  
  for( i in 1:(length(series)-(trainingSize + horizon) + 1))
  {
    
    forecasts = fore.aruma.wge(series[i:(i+(trainingSize-1))],phi = phis, theta = thetas, s = s, d = d,n.ahead = horizon)
    
    ASE = mean((series[(trainingSize+i):(trainingSize+ i + (horizon) - 1)] - forecasts$f)^2)
    
    ASEHolder[i] = ASE
    
  }
  
  ASEHolder
  hist(ASEHolder)
  WindowedASE = mean(ASEHolder)
  
  print("The Summary Statistics for the Rolling Window ASE Are:")
  print(summary(ASEHolder))
  print(paste("The Rolling Window ASE is: ",WindowedASE))
  return(WindowedASE)
}

#ARMA Rolling ASE
Rolling_Window_ASE(hk.ind, phis = est.hk.ind$phi,thetas = est.hk.ind$theta, horizon = 365, trainingSize = 500) 

#The Short Term Rolling Window ASE is: 1677.426


#ARIMA rOLLING ASE
Rolling_Window_ASE(hk.ind, d=2, s = 365, phis = est.hk.ind$phi,thetas = est.hk.ind$theta, horizon = 1825, trainingSize = 1000) 

#The Short Term Rolling Window ASE is: 38524175


```


Price Index compare generated realizations. 
```{r Price Index Final Model, echo=FALSE}
### Testing parameterized model estimates

#Compare Generated Realizations and Spectral Densities 

hk.ind.arma.gen = gen.arma.wge(5000,phi = est.hk.ind$phi,theta = est.hk.ind$theta, vara = est.hk.ind$avar)

plotts.sample.wge(hk.ind.arma.gen)


hk.ind.arima.gen = gen.arima.wge(5000,d=2, s=365, phi = est.hk.ind$phi,theta = est.hk.ind$theta, vara = est.hk.ind$avar)

plotts.sample.wge(hk.ind.arima.gen)



#Compare Spectral Densities using parameters from ARIMA(11,2,4) model generated
sims = 2
SpecDen = parzen.wge(hk.ind, plot = "FALSE")
plot(SpecDen$freq,SpecDen$pzgram, type = "l", lwd = 2)

for( i in 1: sims)
{
  SpecDen2 = parzen.wge(gen.arima.wge(10000,d=2, s=365, phi = est.hk.ind$phi,theta = est.hk.ind$theta, vara = est.hk.ind$avar, plot = "FALSE"), plot = "FALSE")
  lines(SpecDen2$freq,SpecDen2$pzgram, lwd = 2, col = "red")
} 

## Estimated parameters from generated model are pretty consistent with with the actual parameters from the data 
```

