---
title: "Hong Kong Macroeconomic Data"
author: "Jason Herbaugh and Alexander Sepenu"
date: "11/13/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(nnfor)
library(forecast)
library(vars)
library(tswge)
library(naniar)
library(DataExplorer)
library(GGally)
```

Data is available from: https://www.kaggle.com/stanley11291985/hk-macroeconomics-data

This data set is economic data for the Hong Kong private housing market collected between 2003 and 2019. The data contains variables connected to the following: 

* Hang Seng Index (total volume and close price)
* Index data for Consumer Price and Private Domestic Housing
* Unemployment Rate and Bank Interest Rate
* Inventory (built/sold/vacant)
* Sales Metrics (quantity/amount)


```{r Hong Kong Macroeconomic CSV Data}
hk_eco <- read.csv(file.choose(), header = TRUE)

head(hk_eco)

hk_eda <- hk_eco

str(hk_eda)

summary(hk_eda)


```


Scatter Plot of columns. All Columns are continous.
```{r GGPAirs, echo=FALSE}
ggpairs(hk_eda[2:14])
```


Univariate analysis on the HSI_Volume column. This is the transaction volume for the Hang Seng Index.
```{r Scale HSI_Volume, echo=FALSE}
#choosing hk_eda$HSI...volume to run Univarate Model
hk <- (hk_eco$HSI_volume)

#scale data by dividing by 1 million to normalize data
hk.scale <- hk_eco$HSI_volume/1000000

#plotting different timeframes in data to game insight
plotts.sample.wge(hk.scale)# True Acf is slowly dumping  with spectral density showing evidence of a wandering behavior at peak f=0 as seen in the realization 
# with a hint of cyclic behavior gives an indication of a dominant (1-B) present hence we proceed to difference the data

# Taking First difference to remove (1-B) from full  scaled data
hk.df1= artrans.wge(hk.scale,phi.tr = 1)#Differencing the data shows that the sample autocorrelation looks white noise  and come cyclic behavior but the realization does not show white noise.
# we will proceed to model the data
```

HSI_Volume model identification
```{r HSI_Volume Model ID, echo=FALSE}
# Model identification for the transformed or difference data using AIC and BIC approach
aic5.wge(hk.df1, p= 0:13, q= 0:5, type = "aic")

aic5.wge(hk.df1, p= 0:13, q= 0:5, type = "bic")

# Since AIC value is lower compared to that of BIC, we use ARMA(3,4) from the AIC results


```

HSI_Volume estimate coefficients for model. 
```{r HSI_Volume Final Model, echo=FALSE}
# Use estimate p & q to get estimates of phi and thetas
est.hk <- est.arma.wge(hk.df1,p=3, q=4)

est.hk$avar

mean(hk.scale)

#Final Model
# (1-B)(1 + 0.462B - 0.060B^2 + 0.633B^3)(X_t + 1492.191) = (1 - 0.121B - 0.447B^2 - 0.705B^3 + 0.327B^4)a_t  $avar = 256933.7


```

HSI_Volume model forecasts
```{r HSI_Volume model forecast, echo=FALSE}
########### forecast model forward 1000 volumes into future

#ARMA(3,4)
fore.arma.wge(hk.scale, phi = est.hk$phi,theta = est.hk$theta, n.ahead = 180, lastn = FALSE,limits = FALSE)


#ARIMA(3,1,4)
fore.aruma.wge(hk.scale,d=1,est.hk$phi,theta = est.hk$theta, n.ahead = 180, lastn = FALSE,limits = FALSE)



```

HSI_Volume model ASE
```{r HSI_Volume model ASE, echo=FALSE}
# Calculating ASE for Last 180 observations
n = 180
x = hk.scale
x.pred.scale = fore.arma.wge(hk.scale, phi = est.hk$phi,theta = est.hk$theta, n.ahead = 180, lastn = FALSE,limits = FALSE)
ASE.scale = mean((x[(length(x)-n+1):(length(x))]-x.pred.scale$f)^2)
print(paste0('ASE: ',round(ASE.scale,2)))

#ARMA ASE: 252237.46



# Calculating ASE for Last 180 observations of ARIMA model
n = 180
x = hk.scale
x.pred.scale1 = fore.aruma.wge(hk.scale,d=1,est.hk$phi,theta = est.hk$theta, n.ahead = 180, lastn = FALSE,limits = FALSE)
ASE.scale1 = mean((x[(length(x)-n+1):(length(x))]-x.pred.scale1$f)^2)
print(paste0('ASE: ',round(ASE.scale1,2)))

#ARIMA ASE: 233115.11


#Rolling Window ASE

Rolling_Window_ASE = function(series, trainingSize, horizon = 1, s = 0, d = 0, phis = 0, thetas = 0)
{
  ASEHolder = numeric()
  
  for( i in 1:(length(series)-(trainingSize + horizon) + 1))
  {
    
    forecasts = fore.aruma.wge(series[i:(i+(trainingSize-1))],phi = phis, theta = thetas, s = s, d = d,n.ahead = horizon)
    
    ASE = mean((series[(trainingSize+i):(trainingSize+ i + (horizon) - 1)] - forecasts$f)^2)
    
    ASEHolder[i] = ASE
    
  }
  
  ASEHolder
  hist(ASEHolder)
  WindowedASE = mean(ASEHolder)
  
  print("The Summary Statistics for the Rolling Window ASE Are:")
  print(summary(ASEHolder))
  print(paste("The Rolling Window ASE is: ",WindowedASE))
  return(WindowedASE)
}


Rolling_Window_ASE(hk.scale, s = 12, phis = est.hk$phi, horizon = 15, trainingSize = 100) 

```

Univariate analysis on the HSI Private Domestic Price Index This is the Price Index of private housing in Hong Kong.
```{r Price_Index , echo=FALSE}
hk_ind <- hk_eda$Private_Domestic.Price_Index.


#plotting different time frames in data to game insight
plotts.sample.wge(hk_ind)# realization is shows wandering behavior with no sign of cyclic behavior
# it also has its True sample autocorrelation showing identical rho_k = 1
#spectral density shows a dominant (1-B) behavior at peak f=0 hence an indication for an ARIMA model we then proceed to take the first different 

# Taking First difference to remove (1-B) from full  scaled data
hk.ind.df1= artrans.wge(hk_ind,phi.tr = 1) # Taking the first difference of the data (1-B) to stationarize the data

acf(hk.ind.df1) # Acfs are slowing dumping with a slight hint of cyclic behavior

hk.ind.df2= artrans.wge(hk.ind.df1,phi.tr = 1) #taking the second difference of the first difference (1-B)^2 shows significance at lag 1 with hint of cyclic behavior

hk.ind.df3 = artrans.wge(hk.ind.df2, phi.tr = c(rep(0,11),1))# taking the 12th difference of the data (1-B^12) to stationarize the data but shows seasonality at lag 12 
#hence we remove the seasonality in the data with this differencing like in the airline model

plotts.sample.wge(hk.ind.df3) # sample Autocorrelations shows seasonal behavior at lag 12 
#spectral density of the realization has no peak at f=o but has 8 peaks between f=0 and f=0.5

parzen.wge(hk.ind.df3) # wander with a strong indication of cyclic behavior
```

Price Index estimate coefficients for model. 
```{r Price_Index Model, echo=FALSE}
# Use estimate p & q to get estimates of phi and thetas
est.hk.ind <- est.arma.wge(hk.ind.df3,p=12, q=5)

est.hk.ind$avar

mean(hk_ind)

#Final Model
# (1-B)^2 (1-B^12)(1 -0.0065B - 0.0053B^2 + 0.0581B^3 + 0.2819B^4 + 0.2321B^5 + 0.2023B^6 + 0.1594B^7 + 0.1309B^8 + 0.1402B^9 + 0.0337^10 - 0.0020B^11 + 0.4638B^12)(X_t + 197.065) = (1 - 1.7602B + 0.7959B^2 + 0.0444B^3 - 0.2856B^4)a_t  $avar = 0.0955


```

Price Index model forecasts and ASE
```{r Price_Index ASE, echo=FALSE}

# Calculating ASE for Last 180 observations
n = 180
x = hk_ind
x.pred.ind = fore.arma.wge(hk_ind, phi = est.hk.ind$phi,theta = est.hk.ind$theta, n.ahead = 180, lastn = FALSE,limits = FALSE)
ASE.ind = mean((x[(length(x)-n+1):(length(x))]-x.pred.ind$f)^2)
print(paste0('ASE: ',round(ASE.ind,2)))

#ARMA ASE: 313876.36



# Calculating ASE for Last 180 observations using ARIMA Model
n = 180
x = hk_ind
x.pred.ind1 = fore.aruma.wge(hk_ind,d=1,phi= est.hk.ind$phi,theta = est.hk.ind$theta, n.ahead = 180, lastn = TRUE,limits = FALSE)
ASE.ind1 = mean((x[(length(x)-n+1):(length(x))]-x.pred.ind1$f)^2)
print(paste0('ASE: ',round(ASE.ind1,2)))

#ARIMA ASE: 1738977.48


Rolling_Window_ASE(hk_ind, s = 12, phis = est.hk.ind$phi,theta = est.hk.ind$theta, horizon = 15, trainingSize = 1000) 



```

